PLUNGER: Reproducing FLUSH+RELOAD: A High-Resolution, Low-Latency Side Channel Attack On GnuPG

### 2014-12-17 paper/paper.tex
Fix tpyo (multiple -> multiply)

Of interest is the algorithm used to compute $c^d\ mod\ N$. This is known as the
problem of modular exponentiation. The most straightforward method of performing
modular exponentiation is to reduce modulo $N$ after each multiplication. This
would then take $O(d)$ multiplications. However, there exists a much more
efficient algorithm known as Square-and-Multiply\cite{Knuth:1997:ACP:270146}.
This method is derived from the binary representation of the exponent $d$.
Consider $d = \sum_{i=0}^{n-1}x_i 2^i$. Then $c^d = c^{(\sum_{i=0}^{n-1}x_i
2^i)} = \prod_{i=0}^{n-1}c^{x_i 2^i}$. Then reducing modulo $N$ we obtain
$m$ as desired. The following code shows GnuPG 1.4.13's implementation of
Square-and-Multiply. We can proceed to implement the algorithm by scanning the
binary representation of $d$ from right to left. If the bit is $1$, we will
multiply and then square, and if the bit is a $0$, we will just square.
Inserting reduces to keep memory use manageble, we see that when the bit is $1$,
we will square, reduce, multiple, and reduce, and when the bit is $0$, we will
only square and reduce.

>>>>

Of interest is the algorithm used to compute $c^d\ mod\ N$. This is known as the
problem of modular exponentiation. The most straightforward method of performing
modular exponentiation is to reduce modulo $N$ after each multiplication. This
would then take $O(d)$ multiplications. However, there exists a much more
efficient algorithm known as Square-and-Multiply\cite{Knuth:1997:ACP:270146}.
This method is derived from the binary representation of the exponent $d$.
Consider $d = \sum_{i=0}^{n-1}x_i 2^i$. Then $c^d = c^{(\sum_{i=0}^{n-1}x_i
2^i)} = \prod_{i=0}^{n-1}c^{x_i 2^i}$. Then reducing modulo $N$ we obtain
$m$ as desired. The following code shows GnuPG 1.4.13's implementation of
Square-and-Multiply. We can proceed to implement the algorithm by scanning the
binary representation of $d$ from right to left. If the bit is $1$, we will
multiply and then square, and if the bit is a $0$, we will just square.
Inserting reduces to keep memory use manageble, we see that when the bit is $1$,
we will square, reduce, multiply, and reduce, and when the bit is $0$, we will
only square and reduce.
